Today, most often, technical data sheets coupled with the knowledge of a number of unique experienced individuals are used to determine when maintenance is required for the asset. 
Product quality only becomes an issue when customers start complaining and repairs are done when it's already far too late.
All of these puts tremendous strain on the people responsible for the asset, while it could be avoided.
Unexpected shutdowns are costly and very demanding for the workforce involved; a possible solution would be making assets smart in order to increase the availability.
The only way to validate the actual health is by having a continuous look at a broad data set and adding a specific multi-aspect monitoring setup 
consisting of different sensor types that follow the behaviour of the asset's general state-of-health.
\subsection{About the company}
Zensor \cite{Misc:zensor_official_website} provides full, integrated and intelligent monitoring solutions for the industrial production, renewable energy and infrastructure sectors.
This allows to Zensor's customers to convert the potential contained in the world of IoT and Industry 4.0 into their reality. 
The company enable digitalization, but with an interface oriented towards the real human: an expert solution without the need for internal experts.
It provides not only monitoring devices or data analysis, but offers a full, standardized and standalone end-to-end product that leverages the value contained in a subset of the following aspects:
\begin{itemize}
    \item operational efficiency
    \item predictive maintenance
    \item energy efficiency
    \item ageing and degradation
    \item safety 
\end{itemize}
A standard offering consists in several aspects (if required) ordered logically below; as such Zensor takes end-to-end responsibility in monitoring the health and efficiency of structures and processes.
\begin{enumerate}
    \item Hardware \{sensors and acquisition units\}
    \item Installation and Commissioning \{engineering and CAD\}
    \item Data Management \{data transfer, storage, coupling to existing data sources (SCADA, weather, operational...), data cleaning and treatment\}
    \item Analysis and Reporting \{predictions, trend and event detection, real-time reporting through online dashboards.\}
\end{enumerate}
\begin{table}[ht]
    \caption{Assets, Industries, and Infrastructure for which Zensor has specific products}
    \begin{tabular}{@{}lll@{}}
    \toprule
    Asset                 & Industries                       & Infrastructure                       \\ \midrule
    Rolling cranes        & Metal Production                 & Offshore wind                        \\
    Grinders and crushers & Mining and Materials             & Rail                                 \\
    Flattener rollers     & Food Production                  & Civil Infrastructure                 \\
    Rolling mills         & Glass Production                 & Energy                               \\
    Conveyor belts        & Discrete Manufacturing                                                  \\
    Tunnels               & Textiles                                                                \\
    Chain transporters    &                                                                         \\
    Sieves                &                                                                         \\
    Bridges               &                                                                         \\ \bottomrule
\end{tabular}
\end{table}
\subsection{Philosophy}
\paragraph{Vision} 
Technological advance can only bring real value to society when the user-facing component is driven by Simplicity and Clarity for the end-user. 
Zensor sees this as the fastest and most certain route to a world where man-made structures affect the sustainability of our planet in the least possible way:
\begin{enumerate}
    \item they are intrinsically safe;
    \item their useful life is optimized to the maximum;
    \item their impact on environment and society is quantified and communicated.
\end{enumerate}

\paragraph{Mission}
Translate technological innovations in monitoring and analysis into easy-to-understand, tangible and relevant information that we share in the way tailored for either production managers, management, or maintenance professionals \dots
As such, we are the knowledgeable and easy-to-reach companion for owners and operators in making their assets increasingly safe, efficient and sustainable. If up to us, till eternity.
